---
title: "R Notebook"
output: html_notebook
---

TODO:
- It seems like INLA is interpreting the barrel indicators being 0,1,2 as factor levels rather than multiples of a parameter. I may need to specify the model = "z" again to force the parameters to be what I desire. I should check how the results compare when using this (with interactions included)
- Calculate posterior predictive p-value for the average (and variance?) CMC count for comparison between two barrels. Our primary interest is at the barrel-level, so we would like the mean and variance to be similar to the mean and variance to be similar to observed mean and variance for each barrel comparison. This should look better than the scan-specific posterior predictive p-value.
- Figure out best way to show credible intervals for different parameters
- Pull together convergence diagnostic statistics/plot for INLA
- Calculate error rate estimates using simulated data. Compare to error rate from regular CMC method used on the same scans with same threshold.


```{r setup}
library(tidyverse)
library(INLA)
```


```{r}
load("originalMethodCMCs.RData")

originalMethodCMCs_full <- originalMethodCMCs %>%
  dplyr::select(cellID,originalMethodClassif,comparisonName) %>%
  mutate(originalMethodClassif = unlist(ifelse(originalMethodClassif == "CMC",1,0)),
         cellID = unlist(cellID)) %>%
  as.data.frame() %>%
  # arrange(comparisonName,cellID) %>%
  tidyr::separate(col = comparisonName,into = c("reference","target"),sep = " vs. ",remove = FALSE) %>%
  dplyr::filter(reference != target) %>%
  mutate(refBarrel = str_sub(reference,-2,-2),
         targBarrel = str_sub(target,-2,-2),
         type = ifelse(refBarrel == targBarrel,"match","non-match"))
```

```{r}
scanIndicator <- map_dfc(unique(c(originalMethodCMCs_full$reference,originalMethodCMCs_full$target)),
                         function(scan){
                           
                           originalMethodCMCs_full %>%
                             mutate(scan = ifelse(reference == scan | target == scan,1,0)) %>%
                             dplyr::select(scan) %>%
                             set_names(scan)
                           
                         })

barrelIndicator <- map_dfc(unique(c(originalMethodCMCs_full$refBarrel,originalMethodCMCs_full$targBarrel)),
                           function(barrel){
                             
                             originalMethodCMCs_full %>%
                               mutate(ret = ifelse(refBarrel == barrel & targBarrel == barrel,2,
                                                   ifelse(refBarrel == barrel | targBarrel == barrel,1,0))) %>%
                               dplyr::select(ret) %>%
                               set_names(paste0(barrel))
                             
                             # originalMethodCMCs_full %>%
                             #   mutate(ref = ifelse(refBarrel == barrel,1,0),
                             #          targ = ifelse(targBarrel == barrel,1,0)) %>%
                             #   dplyr::select(ref,targ) %>%
                             #   set_names(paste0("ref_",barrel),paste0("targ_",barrel))
                             
                           })
```

```{r}
originalMethodCMCs_grid <- expand.grid(colInd = 1:8,rowInd = 1:8) %>%
  mutate(cellID = 1:64)

adjacent <- matrix(0,nrow = nrow(originalMethodCMCs_grid),ncol = nrow(originalMethodCMCs_grid))

for(ind in 1:nrow(originalMethodCMCs_grid)){
  
  #determine cells that are adjacent (including diagonal) with the cell of interest
  dat <- originalMethodCMCs_grid %>%
    dplyr::filter((abs(rowInd - originalMethodCMCs_grid[ind,]$rowInd) == 1 & abs(colInd - originalMethodCMCs_grid[ind,]$colInd) == 0) | 
                    (abs(rowInd - originalMethodCMCs_grid[ind,]$rowInd) == 0 & abs(colInd - originalMethodCMCs_grid[ind,]$colInd) == 1) |
                    ((abs(rowInd - originalMethodCMCs_grid[ind,]$rowInd) == 1 & abs(colInd - originalMethodCMCs_grid[ind,]$colInd) == 1)))
  
  #update adjacency matrix to define an edge between adjacent cells
  for(i in 1:nrow(dat)){
    
    adjacent[originalMethodCMCs_grid[ind,]$cellID,dat[i,]$cellID] <- 1
    adjacent[dat[i,]$cellID,originalMethodCMCs_grid[ind,]$cellID] <- 1
    
  }
  
}

g = inla.read.graph(adjacent)
```

```{r}
scanIndicator <- map_dfc(unique(c(originalMethodCMCs_full %>%
                                    filter(refBarrel != "N" & targBarrel != "N") %>%
                                    filter(refBarrel != "B" & targBarrel != "B") %>%
                                    filter(refBarrel != "A" & targBarrel != "A") %>%
                                    filter(refBarrel != "C" & targBarrel != "C") %>%
                                    filter(refBarrel != "Z" & targBarrel != "Z") %>%
                                    filter(refBarrel != "W" & targBarrel != "W") %>%
                                    pull(reference),
                                  originalMethodCMCs_full %>%
                                    filter(refBarrel != "N" & targBarrel != "N") %>%
                                    filter(refBarrel != "B" & targBarrel != "B") %>%
                                    filter(refBarrel != "A" & targBarrel != "A") %>%
                                    filter(refBarrel != "C" & targBarrel != "C") %>%
                                    filter(refBarrel != "Z" & targBarrel != "Z") %>%
                                    filter(refBarrel != "W" & targBarrel != "W") %>%
                                    pull(target))),
                         function(scan){
                           
                           originalMethodCMCs_full %>%
                             mutate(scan = ifelse(reference == scan | target == scan,1,0)) %>%
                             dplyr::select(scan) %>%
                             set_names(scan)
                           
                         })
```



```{r}
inlaFit_barrelRandomInteraction_full_initial <- 
  INLA::inla(formula = originalMethodClassif ~ 
               -1 + 
               # (barrelG + barrelC + barrelA + barrelZ + barrelR)^2 +
               f(barrelG,model = "iid") +
               f(barrelF,model = "iid") +
               f(barrelU,model = "iid") +
               f(barrelR,model = "iid") +
               # f(barrelN,model = "iid") +
               # f(barrelB,model = "iid") +
               # f(barrelC,model = "iid") +
               # f(barrelA,model = "iid") +
               # f(barrelZ,model = "iid") +
               # f(barrelW,model = "iid") +
               f(barrelGbarrelF,model = "iid") +
               f(barrelGbarrelU,model = "iid") +
               f(barrelGbarrelR,model = "iid") +
               # f(barrelGbarrelN,model = "iid") +
               # f(barrelGbarrelB,model = "iid") +
               # f(barrelGbarrelC,model = "iid") +
               # f(barrelGbarrelA,model = "iid") +
               # f(barrelGbarrelZ,model = "iid") +
               # f(barrelGbarrelW,model = "iid") +
               f(barrelFbarrelU,model = "iid") +
               f(barrelFbarrelR,model = "iid") +
               # f(barrelFbarrelN,model = "iid") +
               # f(barrelFbarrelB,model = "iid") +
               # f(barrelFbarrelC,model = "iid") +
               # f(barrelFbarrelA,model = "iid") +
               # f(barrelFbarrelZ,model = "iid") +
               # f(barrelFbarrelW,model = "iid") +
               f(barrelUbarrelR,model = "iid") +
               # f(barrelUbarrelN,model = "iid") +
               # f(barrelUbarrelB,model = "iid") +
               # f(barrelUbarrelC,model = "iid") +
               # f(barrelUbarrelA,model = "iid") +
               # f(barrelUbarrelZ,model = "iid") +
               # f(barrelUbarrelW,model = "iid") +
               # f(barrelRbarrelN,model = "iid") +
               # f(barrelRbarrelB,model = "iid") +
               # f(barrelRbarrelC,model = "iid") +
               # f(barrelRbarrelA,model = "iid") +
               # f(barrelRbarrelZ,model = "iid") +
             # f(barrelRbarrelW,model = "iid") +
             # f(barrelNbarrelB,model = "iid") +
             # f(barrelNbarrelC,model = "iid") +
             # f(barrelNbarrelA,model = "iid") +
             # f(barrelNbarrelZ,model = "iid") +
             # f(barrelNbarrelW,model = "iid") +
             # f(barrelBbarrelC,model = "iid") +
             # f(barrelBbarrelA,model = "iid") +
             # f(barrelBbarrelZ,model = "iid") +
             # f(barrelBbarrelW,model = "iid") 
             # f(barrelCbarrelA,model = "iid") +
             # f(barrelCbarrelZ,model = "iid") +
             # f(barrelCbarrelW,model = "iid") +
             # f(barrelAbarrelZ,model = "iid") +
             # f(barrelAbarrelW,model = "iid") +
             # f(barrelZbarrelW,model = "iid") +
             f(scanID,model = "z",Z = as.matrix(scanIndicator),constr = TRUE) +
               f(cellID,model = "besag",graph = g),
             family = "binomial",
             Ntrials = 1,
             data = originalMethodCMCs_full %>%
               dplyr::select(cellID,originalMethodClassif,refBarrel,targBarrel) %>%
               mutate(refBarrel = factor(refBarrel),
                      targBarrel = factor(targBarrel)) %>%
               mutate(scanID = rep(1:(nrow(.)/64),each = 64),
                      barrelID = rep(1:(nrow(.)/64),each = 64)) %>%
               bind_cols(barrelIndicator %>%
                           set_names(paste0("barrel",names(barrelIndicator)))) %>%
               mutate(barrelGbarrelF = barrelG*barrelF,
                      barrelGbarrelU = barrelG*barrelU,
                      barrelGbarrelR = barrelG*barrelR,
                      barrelGbarrelN = barrelG*barrelN,
                      barrelGbarrelB = barrelG*barrelB,
                      barrelGbarrelC = barrelG*barrelC,
                      barrelGbarrelA = barrelG*barrelA,
                      barrelGbarrelZ = barrelG*barrelZ,
                      barrelGbarrelW = barrelG*barrelW,
                      barrelFbarrelU = barrelF*barrelU,
                      barrelFbarrelR = barrelF*barrelR,
                      barrelFbarrelN = barrelF*barrelN,
                      barrelFbarrelB = barrelF*barrelB,
                      barrelFbarrelC = barrelF*barrelC,
                      barrelFbarrelA = barrelF*barrelA,
                      barrelFbarrelZ = barrelF*barrelZ,
                      barrelFbarrelW = barrelF*barrelW,
                      barrelUbarrelR = barrelU*barrelR,
                      barrelUbarrelN = barrelU*barrelN,
                      barrelUbarrelB = barrelU*barrelB,
                      barrelUbarrelC = barrelU*barrelC,
                      barrelUbarrelA = barrelU*barrelA,
                      barrelUbarrelZ = barrelU*barrelZ,
                      barrelUbarrelW = barrelU*barrelW,
                      barrelRbarrelN = barrelR*barrelN,
                      barrelRbarrelB = barrelR*barrelB,
                      barrelRbarrelC = barrelR*barrelC,
                      barrelRbarrelA = barrelR*barrelA,
                      barrelRbarrelZ = barrelR*barrelZ,
                      barrelRbarrelW = barrelR*barrelW,
                      barrelNbarrelB = barrelN*barrelB,
                      barrelNbarrelC = barrelN*barrelC,
                      barrelNbarrelA = barrelN*barrelA,
                      barrelNbarrelZ = barrelN*barrelZ,
                      barrelNbarrelW = barrelN*barrelW,
                      barrelBbarrelC = barrelB*barrelC,
                      barrelBbarrelA = barrelB*barrelA,
                      barrelBbarrelZ = barrelB*barrelZ,
                      barrelBbarrelW = barrelB*barrelW,
                      barrelCbarrelA = barrelC*barrelA,
                      barrelCbarrelZ = barrelC*barrelZ,
                      barrelCbarrelW = barrelC*barrelW,
                      barrelAbarrelZ = barrelA*barrelZ,
                      barrelAbarrelW = barrelA*barrelW,
                      barrelZbarrelW = barrelZ*barrelW) %>%
               filter(refBarrel != "N" & targBarrel != "N") %>%
               filter(refBarrel != "B" & targBarrel != "B") %>%
               filter(refBarrel != "A" & targBarrel != "A") %>%
               filter(refBarrel != "C" & targBarrel != "C") %>%
               filter(refBarrel != "Z" & targBarrel != "Z") %>%
               filter(refBarrel != "W" & targBarrel != "W"),
             control.compute = list(dic = TRUE,cpo = TRUE,waic = TRUE,config = TRUE)
             # ,verbose = TRUE
             ,num.threads = 2
             # ,control.predictor = list(A = as.matrix(barrelIndicator))
             ,control.inla = list(#diagonal = 10,
               strategy = "gaussian",int.strategy = "eb")
  )

originalMethodCMCs_entireFourBarrels <- originalMethodCMCs_full %>%
  filter(refBarrel != "N" & targBarrel != "N") %>%
  filter(refBarrel != "B" & targBarrel != "B") %>%
  filter(refBarrel != "A" & targBarrel != "A") %>%
  filter(refBarrel != "C" & targBarrel != "C") %>%
  filter(refBarrel != "Z" & targBarrel != "Z") %>%
  filter(refBarrel != "W" & targBarrel != "W") 

save(originalMethodCMCs_entireFourBarrels,file = "originalMethodCMCs_entireFourBarrels.RData")

save(inlaFit_barrelRandomInteraction_full_initial,file = "inlaFit_barrelRandomInteraction_full_initial.RData")
```

```{r}
load("inlaFit_barrelRandomInteraction_full_initial.RData")

summary(inlaFit_barrelRandomInteraction_full_initial)

inlaFit_barrelRandomInteraction_full_initial$summary.random
```


```{r}
inlaFit_barrelRandomInteraction_full_initial$summary.random %>%
  map(function(dat){
    
    ggplot(data = dat,aes(x = ID,y = mean)) +
      geom_point() +
      geom_hline(yintercept = 0)
    
  })
```

```{r}
INLAutils::plot_fixed_marginals(inlaFit_barrelRandomInteraction_full_initial,priors = TRUE) 

INLAutils::plot_hyper_marginals(inlaFit_barrelRandomInteraction_full_initial)

plt <- INLAutils::plot_marginals_fitted(inlaFit_barrelRandomInteraction_full_initial)

# plt

plt$data %>%
  filter(plot == "Fitted Values") %>%
  filter(mean > 0) %>%
  ggplot(aes(x = ID,y = mean)) +
  geom_point()

INLAutils::plot_random_effects(inlaFit_barrelRandomInteraction_full_initial,type = "line")
```


```{r}
inlaFit_barrelRandomInteraction_full_initial$marginals.random %>%
  .[1:10] %>%
  map2(.y = names(.),
       function(dat,name){
         
         if(length(dat) == 3){
           
           plt <- ggplot(data = dat %>%
                           map_dfr(~ as.data.frame(.x)) %>%
                           mutate(ind = as.factor(rep(1:3,each = nrow(.)/3))),
                         aes(x=x,y=y)) +
             geom_line(aes(group = ind,colour = ind)) +
             labs(title = name)
           
         }
         if(length(dat) == 2){
           
           plt <- ggplot(data = dat %>%
                           map_dfr(~ as.data.frame(.x)) %>%
                           mutate(ind = as.factor(rep(1:2,each = nrow(.)/2))),
                         aes(x=x,y=y)) +
             geom_line(aes(group = ind,colour = ind)) +
             labs(title = name)
           
         }
         
         return(plt)
         
       })
```

```{r}
originalMethodCMCs_full %>%
  dplyr::select(cellID,originalMethodClassif,refBarrel,targBarrel) %>%
  mutate(refBarrel = factor(refBarrel),
         targBarrel = factor(targBarrel)) %>%
  mutate(scanID = rep(1:(nrow(.)/64),each = 64),
         barrelID = rep(1:(nrow(.)/64),each = 64)) %>%
  bind_cols(barrelIndicator %>%
              set_names(paste0("barrel",names(barrelIndicator)))) %>%
  filter(refBarrel != "N" & targBarrel != "N") %>%
  filter(refBarrel != "B" & targBarrel != "B") %>%
  filter(refBarrel != "A" & targBarrel != "A") %>%
  filter(refBarrel != "C" & targBarrel != "C") %>%
  filter(refBarrel != "Z" & targBarrel != "Z") %>%
  filter(refBarrel != "W" & targBarrel != "W") %>%
  mutate(postMean = inlaFit_barrelRandomInteraction_full_initial$summary.fitted.values %>%
           pull(mean)) %>%
  filter(!is.na(originalMethodClassif)) %>%
  arrange(targBarrel,refBarrel) %>%
  mutate(barrels = paste0(refBarrel,targBarrel),
         rowID = 1:nrow(.)) %>%
  ggplot(aes(x=rowID,y=postMean,colour=targBarrel,shape = refBarrel)) +
  geom_point() +
  # theme(legend.position = "none")
  theme_bw()
```

```{r}
repData <- originalMethodCMCs_full %>%
  filter(refBarrel != "N" & targBarrel != "N") %>%
  filter(refBarrel != "B" & targBarrel != "B") %>%
  filter(refBarrel != "A" & targBarrel != "A") %>%
  filter(refBarrel != "C" & targBarrel != "C") %>%
  filter(refBarrel != "Z" & targBarrel != "Z") %>%
  filter(refBarrel != "W" & targBarrel != "W") %>%
  select(comparisonName,originalMethodClassif,type)

simulatedResults <- map_dfr(1:100,
                            function(rep){
                              
                              # samples parameters from posterior
                              postSample <- INLA::inla.posterior.sample(n = 1,result = inlaFit_barrelRandomInteraction_full_initial)
                              
                              # combines sampled parameter above into linear predictor
                              postPredictor <- INLA::inla.posterior.sample.eval(fun = "Predictor",samples = postSample)
                              
                              # inverse link transforms linear predictor back to probability
                              sampleProbs <- exp(postPredictor)/(1 + exp(postPredictor))
                              
                              repData %>%
                                mutate(sampleProb = c(sampleProbs),
                                       samp = map_dbl(sampleProb,~ rbinom(n = 1,size = 1,prob = .))) %>%
                                mutate(samp = ifelse(is.na(originalMethodClassif),NA,samp)) %>%
                                group_by(comparisonName,type) %>%
                                summarise(sampCount = sum(samp,na.rm = TRUE),.groups = "drop") %>%
                                mutate(postRep = rep)
                              
                            })

simulatedResults <- simulatedResults %>%
  tidyr::separate(col = comparisonName,sep = " vs. ",into = c("reference","target"),remove = FALSE) %>%
  mutate(refBarrel = str_sub(reference,-2,-2),
         targBarrel = str_sub(target,-2,-2))

save(simulatedResults,file = "simulatedResults.RData")

# save(originalMethodCMCs_entireFourBarrels,file = "originalMethodCMCs_entireFourBarrels.RData")

originalMethodCMCs_entireFourBarrels %>% 
  group_by(comparisonName) %>%
  summarise(originalMethod = sum(originalMethodClassif,na.rm = TRUE)) %>%
  arrange(comparisonName) %>%
  separate(col = comparisonName,into = c("reference","target"),sep = " vs. ",remove = FALSE) %>%
  dplyr::filter(reference != target) %>%
  mutate(refBarrel = str_sub(reference,-2,-2),
         targBarrel = str_sub(target,-2,-2),
         type = ifelse(refBarrel == targBarrel,"match","non-match")) %>%
  # dplyr::filter(type == "match") %>%
  ggplot(aes(x = originalMethod,y = ..density..,fill = type)) +
  geom_histogram() +
  facet_wrap(~ type,scales = "free") +
  facet_wrap(refBarrel ~ targBarrel)

simulatedResults %>%
  ggplot(aes(x = sampCount,y = ..density..,fill = type)) +
  geom_histogram() +
  facet_wrap(refBarrel ~ targBarrel)
```

```{r}
simulatedResults %>%
  left_join(originalMethodCMCs_full %>%
              filter(refBarrel != "N" & targBarrel != "N") %>%
              filter(refBarrel != "B" & targBarrel != "B") %>%
              filter(refBarrel != "A" & targBarrel != "A") %>%
              filter(refBarrel != "C" & targBarrel != "C") %>%
              filter(refBarrel != "Z" & targBarrel != "Z") %>%
              filter(refBarrel != "W" & targBarrel != "W") %>%
              group_by(comparisonName) %>%
              summarise(obsCount = sum(originalMethodClassif,na.rm = TRUE)),
            by = "comparisonName") %>%
  group_by(comparisonName,type,refBarrel,targBarrel) %>%
  summarise(pVal = mean(sampCount <= obsCount)) %>%
  ggplot(aes(x=pVal,fill = type)) +
  geom_histogram() +
  facet_wrap(~ type)
```


```{r}
simulatedResults %>%
  mutate(misclass = ifelse((type == "match" & sampCount < 6) | (type == "non-match" & sampCount >= 6),TRUE,FALSE)) %>%
  group_by(type) %>%
  summarise(misclass = mean(misclass))

simulatedResults %>%
  mutate(misclass = ifelse((type == "match" & sampCount < 6) | (type == "non-match" & sampCount >= 6),TRUE,FALSE)) %>%
  pull(misclass) %>%
  mean()
```

































Fit alternative to the model to ensure that the barrel random effects is treated as a single parameter rather than dummy variables using method = "z" and the barrelIndicator matrix

```{r}
load("originalMethodCMCs_entireFourBarrels.RData")

# originalMethodCMCs_entireFourBarrels <- originalMethodCMCs_entireFourBarrels %>%
#   filter(!(refBarrel %in% c("U","R")) & !(targBarrel %in% c("U","R")))

scanIndicator <- map_dfc(unique(c(originalMethodCMCs_entireFourBarrels$reference,originalMethodCMCs_entireFourBarrels$target)),
                         function(scan){
                           
                           originalMethodCMCs_entireFourBarrels %>%
                             mutate(scan = as.integer(ifelse(reference == scan | target == scan,1,0))) %>%
                             dplyr::select(scan) %>%
                             set_names(scan)
                           
                         })



barrelIndicator <- map_dfc(unique(c(originalMethodCMCs_entireFourBarrels$refBarrel,originalMethodCMCs_entireFourBarrels$targBarrel)),
                           function(barrel){
                             
                             originalMethodCMCs_entireFourBarrels %>%
                               mutate(ret = as.integer(ifelse(refBarrel == barrel | targBarrel == barrel,1,NA))) %>%
                               # mutate(ret = ifelse(refBarrel == barrel & targBarrel == barrel,2,
                               #                     ifelse(refBarrel == barrel | targBarrel == barrel,1,0))) %>%
                               dplyr::select(ret) %>%
                               set_names(paste0("barrel",barrel))
                             
                             # originalMethodCMCs_entireFourBarrels %>%
                             #   mutate(ref = ifelse(refBarrel == barrel,1,0),
                             #          targ = ifelse(targBarrel == barrel,1,0)) %>%
                             #   dplyr::select(ref,targ) %>%
                             #   set_names(paste0("ref_",barrel),paste0("targ_",barrel))
                             
                           })

barrelInteractionIndicator <- map_dfc(1:3,
                                      function(colInd1){
                                        
                                        map_dfc((colInd1 + 1):4,
                                                function(colInd2){
                                                  
                                                  data.frame(x = as.integer(c(barrelIndicator[,colInd1])*c(barrelIndicator[,colInd2]))) %>%
                                                    set_names(nm = paste0(names(barrelIndicator)[colInd1],names(barrelIndicator)[colInd2]))
                                                  
                                                })
                                        
                                      })

barrelIndicator <- bind_cols(barrelIndicator,barrelInteractionIndicator)

inlaFit_barrelRandomInteraction_modelz_entireFourBarrelsGFUR_initial <- 
  INLA::inla(formula = originalMethodClassif ~ 
               -1 + 
               # (barrelG + barrelC + barrelA + barrelZ + barrelR)^2 +
               f(barrelG,model = "iid",values = 1) +
               f(barrelF,model = "iid",values = 1) +
               f(barrelU,model = "iid",values = 1) +
               f(barrelR,model = "iid",values = 1) +
               f(barrelGbarrelF,model = "iid",values = 1) +
               f(barrelGbarrelU,model = "iid",values = 1) +
               f(barrelGbarrelR,model = "iid",values = 1) +
               f(barrelFbarrelU,model = "iid",values = 1) +
               f(barrelFbarrelR,model = "iid",values = 1) +
               f(barrelUbarrelR,model = "iid",values = 1) +
             f(scanID,model = "z",Z = as.matrix(scanIndicator),constr = TRUE) +
               f(cellID,model = "besag",graph = g),
             family = "binomial",
             Ntrials = 1,
             data = originalMethodCMCs_entireFourBarrels %>%
               dplyr::select(cellID,originalMethodClassif) %>%
               mutate(scanID = rep(1:(nrow(.)/64),each = 64)) %>%
               bind_cols(barrelIndicator) %>%
               mutate(originalMethodClassif = as.integer(originalMethodClassif)),
             control.compute = list(dic = TRUE,cpo = TRUE,waic = TRUE,config = TRUE)
             # ,verbose = TRUE
             ,num.threads = 2
             # ,control.predictor = list(A = as.matrix(barrelIndicator))
             ,control.inla = list(#diagonal = 10,
               strategy = "gaussian",int.strategy = "eb")
  )

save(inlaFit_barrelRandomInteraction_modelz_entireFourBarrelsGFUR_initial,
     file = "inlaFit_barrelRandomInteraction_modelz_entireFourBarrelsGFUR_initial.RData")
```




```{r}
inlaFit_barrelRandomInteraction_modelz_entireFourBarrelsGFUR_initial$marginals.random[1:10] %>%
  map(function(dat){
    
    map_dfr(dat,
        function(dat1){
          
          as.data.frame(dat1)
          
        }) %>%
      mutate(ind = 1) %>%
      # mutate(ind = factor(rep(c(0,1),each = nrow(.)/2))) %>%
            ggplot(aes(x=x,y=y,group = ind,colour = ind)) +
            geom_line()
    
  })
```

```{r}
originalMethodCMCs_entireFourBarrels %>%
  group_by(reference,target,refBarrel,targBarrel,type) %>%
  summarise(count = sum(originalMethodClassif,na.rm = TRUE)) %>%
  ggplot(aes(x=count)) +
  geom_histogram(binwidth = 1) +
  facet_wrap(refBarrel ~ targBarrel)
```

```{r}
repData <- originalMethodCMCs_entireFourBarrels %>%
  select(comparisonName,originalMethodClassif,type)

simulatedResults_modelz_entireFourBarrelsGFUR_initial <- map_dfr(1:100,
                            function(rep){
                              
                              # samples parameters from posterior
                              postSample <- INLA::inla.posterior.sample(n = 1,result = inlaFit_barrelRandomInteraction_modelz_entireFourBarrelsGFUR_initial)
                              
                              # combines sampled parameter above into linear predictor
                              postPredictor <- INLA::inla.posterior.sample.eval(fun = "Predictor",samples = postSample)
                              
                              # inverse link transforms linear predictor back to probability
                              sampleProbs <- exp(postPredictor)/(1 + exp(postPredictor))
                              
                              repData %>%
                                mutate(sampleProb = c(sampleProbs),
                                       samp = map_dbl(sampleProb,~ rbinom(n = 1,size = 1,prob = .))) %>%
                                mutate(samp = ifelse(is.na(originalMethodClassif),NA,samp)) %>%
                                group_by(comparisonName,type) %>%
                                summarise(sampCount = sum(samp,na.rm = TRUE),.groups = "drop") %>%
                                mutate(postRep = rep)
                              
                            })

simulatedResults_modelz_entireFourBarrelsGFUR_initial <- simulatedResults_modelz_entireFourBarrelsGFUR_initial %>%
  tidyr::separate(col = comparisonName,sep = " vs. ",into = c("reference","target"),remove = FALSE) %>%
  mutate(refBarrel = str_sub(reference,-2,-2),
         targBarrel = str_sub(target,-2,-2))

save(simulatedResults_modelz_entireFourBarrelsGFUR_initial,file = "simulatedResults_modelz_entireFourBarrelsGFUR_initial.RData")

# save(originalMethodCMCs_entireFourBarrels,file = "originalMethodCMCs_entireFourBarrels.RData")

originalMethodCMCs_entireFourBarrels %>% 
  group_by(comparisonName) %>%
  summarise(originalMethod = sum(originalMethodClassif,na.rm = TRUE)) %>%
  arrange(comparisonName) %>%
  separate(col = comparisonName,into = c("reference","target"),sep = " vs. ",remove = FALSE) %>%
  dplyr::filter(reference != target) %>%
  mutate(refBarrel = paste0("Barrel ",str_sub(reference,-2,-2)),
         targBarrel = paste0("Barrel ",str_sub(target,-2,-2)),
         type = ifelse(refBarrel == targBarrel,"match","non-match")) %>%
  # dplyr::filter(type == "match") %>%
  ggplot(aes(x = originalMethod,y = ..density..,fill = type)) +
  geom_histogram() +
  facet_wrap(~ type,scales = "free") +
  facet_wrap(refBarrel ~ targBarrel) +
  theme_bw()

simulatedResults_modelz_entireFourBarrelsGFUR_initial %>%
  ggplot(aes(x = sampCount,y = ..density..,fill = type)) +
  geom_histogram(binwidth = 1) +
  facet_wrap(refBarrel ~ targBarrel)
```

